Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-25 Final/Final20181223.Rmd
.

In order to see the segmentation of exported products by Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.

@@

* Vehicles other than railway can be classified as a group - the export products we spent too much money

* Machinery, mechanical appliances, electronical machinery and equipments, clothing is another classification - top2 products in terms of money spent

* Third class consist of iron, steel, pearls, ores etc. and this class slightly differs from 4th group in terms of money spent

@@

* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
* Germany and USA are the 2 top countries seen in both directions of trade.
* Generally we have fluctuated trade trend with Russia.
* Turkey's trade deficit analyisis gives the results : 
  + UK gives trade surplus for all years analysed 
  + China, Russia, Germany and USA have the most significant effect on trade deficit
  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
      + Electrical machinery, equipments and machinery, mechanical appliances
      + Mineral fuels, mineral oils and products of their distillation constitute 
      + Vehicles other than railway and mechanical and electronical machinery and equipments
* As a result of clustering exported products;
  + Vehicles other than railway is the group we spent the most money
  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.

>>>>

In order to see the segmentation of exported products from Turkey considering their share in total export value, we implemented k-means clustering method after scaling the export values of each product.

@@

* Vehicles other than railway can be classified as a group - the export products we earned the most money

* Machinery, mechanical appliances, electronical machinery and equipments, clothing is another classification - top2 products in terms of money earned

* Third class consist of iron, steel, pearls, ores etc. and this class slightly differs from 4th group

@@

* Turkeys’ biggest trade partners are China, Germany, Russia and US at import side while they are Germany, UK, Italy and USA at export side. 
* Germany and USA are the 2 top countries seen in both directions of trade.
* Generally we have fluctuated trade trend with Russia.
* Turkey's trade deficit analyisis gives the results : 
  + UK gives trade surplus for all years analysed 
  + China, Russia, Germany and USA have the most significant effect on trade deficit
  + Trade deficit has negatively correlated with USD/TL rate between 2013 and 2016 but there is no relation BIST100 index.
  + Turkey's trade deficit comes from China, Russia, Germany countires and most of deficit comes from products below :
      + Electrical machinery, equipments and machinery, mechanical appliances
      + Mineral fuels, mineral oils and products of their distillation constitute 
      + Vehicles other than railway and mechanical and electronical machinery and equipments
* As a result of clustering exported products;
  + Vehicles other than railway is the group we earned the most money
  + Second group consist of Machinery, mechanical appliances, electronical machinery- equipments and clothing while third one includes iron, steel, pearls, ores etc.
